Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-10 paper/main.tex
Finished with the accuracy on test data. Now will apply to *real* data and that will be it for experiments.
Finished with experiments. Now I will clean up the introductory section and my personal section

\begin{figure}
\centering
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{AlexNet_Accuracy}
  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
  \label{fig:alex_net}
  \end{minipage}\hfill
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{PerClassPerformance}
  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
  \label{fig:per_class}
  \end{minipage}
\end{figure}

@@

\begin{figure}
\centering
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All1000}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}

>>>>

\begin{figure}[t]
\centering
  \begin{minipage}{.48\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{AlexNet_Accuracy1000}
  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
  \label{fig:alex_net}
  \end{minipage}\hfill
  \begin{minipage}{.48\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{PerClassPerformance1000}
  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
  \label{fig:per_class}
  \end{minipage}
\end{figure}

@@

\begin{figure}[t]
\centering
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All1000}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}

Finally, we performed a brief, informal experiment where we applied the neural network to videos that
were not part of our training or testing data. We chose one video for each of the four classes by
searching on Google Video ``X tutorial'' where ``X'' was replaced by one of the four video names.
The first video that was between 5 and 20 minutes long, and that was not already part of our
training/testing data, was selected. We extracted one frame per second for the four videos, and
deleted the first ten and final ten frames from consideration.

To classify the frames, we applied our AlexNet neural network trained on the ``noiseless'' data
after 1000 iterations. To describe the output, we use ``splits'' where $(a,b,c,d)$ indicates that
$a, b, c,$ and $d$ frames were classified as Eclipse, Excel, Photoshop, and SketchUp, respectively.
The splits were as follows: the Eclipse video had $(319,0,79,0)$, the Excel video had
$(610,0,71,7)$, the Photoshop had $(1,6,416,69)$, and the SketchUp had $(9,2,233,804)$. Clearly, for
the Eclipse, Photoshop, and SketchUp videos, the classifer was able to assign the vast majority of
frames to the correct class. If we were using this as part of an overall data mining pipeline, our
classifier would assign the video according to the most-assigned class, so three videos would be
classified correctly.

The Excel output is interesting, because our network thought most of the frames belonged to Eclipse
videos. A brief look at the video indicated that it had an introductory scene that took up ninety
seconds (and we only deleted the first 10 frames) and that it was about a newer version of Excel
(2013) than the ones that were trained in our network (2007). Still, it is unfortunate but shows
that we need to be able to provide a wider variety of training data.
